Certified Knowledge Compilation \\ with Application to Verified Model Counting

### 2023-03-20 doc/mc-paper.tex
add other checkers to related work

>>>>

Verified checkers for unsatisfiability include \cite{Cruz:Filipe:et:al:16,Heule:et:al:17,Lammich:20,Tan:2021}.
The associated proofs add clauses while preserving satisfiability until the empty clause is derived.
In contrast, our proofs construct a new propositional formula, and we have to verify that it
is partitioned and is equivalent to the input.
This requires verifying additional proof steps and subtle invariants, as described in
Sections~\ref{sect:crat} and \ref{section:formally-verified-toolchain}.
